---
title: "Domestic Violence in Colombia: Findings from the DHS"
subtitle: "Final Project"
author: "Sabina Rodriguez Velásquez"
date: "2023-08-08"
output: prettydoc::html_pretty
editor_options: 
chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = 'hide')
```

```{r packages}
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##
## ~ Load Packages ~ ----
##
if(!require(pacman)) install.packages("pacman")
pacman :: p_load(
  dplyr,
  tidyverse,
  janitor,
  here, 
  haven,
  inspectdf,
  cowplot)
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

```{r prepare dataset}
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##
## ~ Load Dataset ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

ir_raw <- haven::read_dta(
  here("data/COIR72FL.DTA"),
    col_select = c(
      v012, #age
      v013, #age group
      v024, #region
      v025, #urban vs. rural
      v106, #highest education
      v131, #ethnicity
      v150, #relationship to hoh
      v151, #sex of hoh
      v190, #wealth
      v501, #marital status
      v502, #union
      v044, #selected for domestic violence
      d104, #emotional violence
      d106, #less severe violence
      d107, #severe violence,
      d108, #sexual violence,
      d109, #first_event_violence,
      d103a, #humiliated
      d103b, #threatened with harm,
      d103c, #insulted,
      d103d, #threat to leave,
      d103e, #threat to take kids
      d105a, #pushed, shook, thrown
      d105b, #slapped
      d105c, #punched
      d105d, #kicked or dragged
      d105e, #strangled
      d105f, #knife
      d115b, #mother violence
      d115c, #father violence
      d115d, #daughterson violence
      d115f, #sibling violence
      d115g, #other relative violence
      d115j, #former partner violence
      d115k, #current bf violence
      d115l, #former bf violence
      d115o, #mother-in-law violence
      d115p, #father-in-law violence
      d115q, #other-in-law violence
      d115v, #teacher violence
      d115w)) #employer violence

##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##
## ~ Rename variables ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
##
ir_renamed <- 
  ir_raw %>% 
  rename(
    age = v012,
    age_group = v013,
    region = v024,
    urban_rural = v025,
    highest_education = v106,
    ethnicity = v131,
    relationship_hoh = v150,
    sex_hoh = v151, 
    wealth_index = v190,
    marital_status = v501, 
    union = v502,
    selected_dv = v044,
    emotional_violence = d104,
    less_severe_violence = d106,
    severe_violence = d107,
    sexual_violence = d108,
    first_event_violence = d109,
    humiliated = d103a,
    threat_harm = d103b, 
    insulted = d103c,
    threat_leave = d103d,
    threat_take_kid = d103e,
    pushed = d105a,
    slapped = d105b,
    punched = d105c,
    kicked = d105d,
    strangled = d105e,
    knife_threat = d105f,
    mother_violence = d115b,
    father_violence = d115c,
    children_violence = d115d,
    sibling_violence = d115f,
    relative_violence = d115g,
    former_partner_violence = d115j,
    current_bf_violence = d115k, 
    former_bf_violence = d115l,
    mother_in_law_violence = d115o,
    father_in_law_violence = d115p,
    other_in_law_violence = d115q,
    teacher_violence = d115v,
    employer_violence = d115w
  )

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Turning variables into factors ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

ir_converted <- 
  ir_renamed %>%
  haven::as_factor() # pass the data frame to as_factor()

```

```{r tools}

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ Tools ~ ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# Color Palette
my_palette <- c("#76c893", "#52b69a", "#34a0a4", "#168aad","#1a759f", "#1e6091", "#184e77")
```

```{r demographic}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Demographics ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# Find out number of observations in survey
num_participants <- 
  nrow(ir_converted) # Total number of women surveyed: 38718

# Find out how many women were interviewed for domestic violence
num_domestic_violence <- 
  ir_converted %>% 
  filter(selected_dv == "woman selected and interviewed") %>% 
  nrow() # Total number of women selected for domestic violence survey

percent_domestic_violence <- 
  round((num_domestic_violence/num_participants)*100, digits = 1)

# Create subset of women who answered domestic violence questions
ir_domestic_violence <- 
  ir_converted %>% 
  filter(selected_dv == "woman selected and interviewed")

# Age
ir_converted %>% 
  summarize(median_age = median(age))

# Region 
ir_converted %>% 
  group_by(region) %>% 
  summarize(num_of_people = n())

# Urban vs. rural 
ir_converted %>% 
  group_by(urban_rural) %>% 
  summarize(num_of_people = n())

# Ethnicity 
ir_converted %>% 
  group_by(ethnicity) %>% 
  summarize(num_of_people = n())

# Highest Education
ir_converted %>% 
  group_by(highest_education) %>% 
  summarize(num_of_people = n())

# Age by Region
ir_converted %>% 
  group_by(region) %>% 
  summarize(num_of_people = n(),
            median_age = median(age))

```

```{r domestic violence}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Domestic Violence ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# Create new variable for emotional violence
ir_domestic_violence <- 
  ir_domestic_violence %>% 
  mutate(exp_emotional_violence = case_when(
    (insulted == "yes, last year" | insulted == "yes, before last year") | (threat_leave == "yes, last year" | threat_leave == "yes, before last year") | (threat_take_kid == "yes, last year" | threat_take_kid == "yes, before last year") ~ "yes",
    insulted == "no" | threat_leave == "never" | threat_take_kid == "no" ~ "no"))

# Create new variable for physical violence
ir_domestic_violence <- 
  ir_domestic_violence %>% 
  mutate(exp_physical_violence = case_when(
    less_severe_violence == "yes" | severe_violence == "yes" ~ "yes",
    less_severe_violence == "no" | severe_violence == "no" ~ "no"))

# Create variable for experience some sort of domestic violence
ir_domestic_violence <- 
  ir_domestic_violence %>% 
  mutate(exp_violence = case_when(
    exp_emotional_violence == "yes" | exp_physical_violence == "yes" | sexual_violence == "yes" ~ "yes",
    exp_emotional_violence == "no" | exp_physical_violence == "no" | sexual_violence == "no" ~ "no"))


# Create small subset of women that experienced some violence
violence <- 
  ir_domestic_violence %>% 
  filter(exp_violence == "yes")

# Create small dataset dropping NA in domestic violence
domestic_violence <- 
  ir_domestic_violence %>% 
  filter(!is.na(exp_violence))

# Create variable for categorizing what type of domestic violence experienced
domestic_violence <- 
  domestic_violence %>% 
  mutate(violence_type = case_when(
    exp_emotional_violence == "yes" & exp_physical_violence == "yes" & sexual_violence == "yes" ~ "emotional, physical, and sexual",
    exp_emotional_violence == "yes" & exp_physical_violence == "yes" ~ "emotional and physical",
    exp_emotional_violence == "yes" & sexual_violence == "yes" ~ "emotional and sexual",
    exp_physical_violence == "yes" & sexual_violence == "yes" ~ "physical and sexual",
    exp_emotional_violence == "yes" ~ "emotional",
    exp_physical_violence == "yes" ~ "physical",
    sexual_violence == "yes" ~ "sexual",
    ))

# Summary Analysis

domestic_violence %>% 
  group_by(exp_violence) %>% 
  summarize(num_of_people = n(),
            percentage = round((n()/nrow(domestic_violence) *100), digits = 1)) # Out of people who had data, 57.4% did not experience any sort of domestic violence

## Calculate number of women who experienced some sort of violence
num_violence <- 
  violence %>% 
  nrow()

## Calculate entire percentage of women who experienced violence
percentage_violence <- 
  round((num_violence/num_domestic_violence)*100, digits = 1)

## Domestic violence by age and age group

domestic_violence %>% 
  group_by(exp_violence) %>% 
  summarize(median_age = median(age)) # Similar distribution of age in people that experience and did not experience domestic violence

domestic_violence %>% 
  group_by(exp_violence, age_group) %>% 
  summarize(count = n(),
            percentage = round((n()/nrow(domestic_violence) *100), digits = 1)) %>% 
  arrange(desc(count), .by_group = TRUE)

## Domestic violence by region 

violence %>% 
  group_by(region) %>% 
  summarize(count = n(),
            percentage = round((n()/nrow(violence) *100), digits = 1))%>% 
  arrange(desc(count), .by_group = TRUE)

## Domestic violence by ethnicity 

violence %>% 
  group_by(ethnicity) %>% 
  summarize(count = n(),
            percentage = round((n()/nrow(violence) *100), digits = 1)) %>% 
  arrange(desc(count), .by_group = TRUE) 

domestic_violence %>% 
  filter(ethnicity == c("indigenous", "black/mulato/afro-colombian/afro-descendant")) %>% 
  group_by(exp_violence, ethnicity) %>% 
  summarize(count = n(),
            percentage = round((n()/nrow(domestic_violence) *100), digits = 1)) %>% 
  arrange(desc(count), .by_group = TRUE) 

## Domestic violence by highest education

violence %>% 
  group_by(highest_education) %>% 
  summarize(count = n(),
            percentage = round((n()/nrow(violence) *100), digits = 1)) %>% 
  arrange(desc(count), .by_group = TRUE)
  

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Perpetrators ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# Create variable for categorizing perpetrator
perpetrator_violence <- 
  domestic_violence %>%
  filter(exp_physical_violence == "yes") %>% 
  mutate(perpetrator = case_when(
    (mother_violence == "yes" | children_violence == "yes" | relative_violence == "yes") & (current_bf_violence == "yes" | former_bf_violence == "yes") ~ "Family and Partners",
    mother_violence == "yes" | children_violence == "yes" | relative_violence == "yes" ~ "Family",
    current_bf_violence == "yes" | former_bf_violence == "yes" ~ "Partners",
    mother_violence == "no" & children_violence == "no" & relative_violence == "no" & current_bf_violence == "no" & former_bf_violence == "no" ~ "No one"
    )) %>% 
  select(mother_violence, children_violence, relative_violence, current_bf_violence, former_bf_violence, perpetrator)


```

```{r plots}

## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Demographic Plots ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

#Total women who answered to experienced domestic violence question
total_violence <- 
  sum(!is.na(ir_domestic_violence$exp_violence))

# Total missing Experienced Domestic Violence question

total_violence_na <-
  sum(is.na(ir_domestic_violence$exp_violence))

## Age Group Stats ----

age_data <- 
  domestic_violence %>% 
  group_by(age_group, exp_violence) %>% 
  count(age_group = factor(age_group)) %>% 
  ungroup() %>% 
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Bar Graph of Age Groups

bargraph_age_group <- 
  ggplot(age_data) + # Use Subset without NA's
  aes(x = age_group, y = n, fill = exp_violence) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = my_palette) +
  geom_text(aes(label = paste0(round(pct, 1),"%")), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            colour = "white", 
            size = 3) +
  labs(x = "Age Group",
       y = "Number of Individulas (n)",
       title = "Domestic Violence across Age Group",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence, total_violence_na)),
       fill = "Domestic Violence?")


## Ethnicity Stats ----

ethnicity_data <- 
  domestic_violence %>% 
  group_by(ethnicity, exp_violence) %>% 
  count(ethnicity = factor(ethnicity)) %>% 
  ungroup() %>% 
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Bar Graph of Ethnicity Groups

bargraph_ethnicity <- 
  ggplot(ethnicity_data) + # Use Subset without NA's
  aes(y = ethnicity, x = n, fill = exp_violence) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = my_palette) +
  geom_text(aes(label = paste0(round(pct, 1),"%")), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            colour = "white", 
            size = 3) +
  labs(x = "Ethnicity",
       y = "Number of Individulas (n)",
       title = "Domestic Violence across Ethnicity",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence, total_violence_na)),
       fill = "Domestic Violence?")


## Rural vs. Urban Stats ----

urban_rural_data <- 
  domestic_violence %>% 
  group_by(urban_rural, exp_violence) %>% 
  count(urban_rural = factor(urban_rural)) %>% 
  ungroup() %>% 
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Bar Graph of Urban vs Rural Groups

bargraph_urban_rural <- 
  ggplot(urban_rural_data) + # Use Subset without NA's
  aes(x = urban_rural, y = n, fill = exp_violence) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = my_palette) +
  geom_text(aes(label = paste0(round(pct, 1),"%")), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            colour = "white", 
            size = 3) +
  labs(x = "Urban vs. Rural",
       y = "Number of Individulas (n)",
       title = "Domestic Violence across Urban vs. Rural",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence, total_violence_na)),
       fill = "Domestic Violence?")


## Wealth Index ----

wealth_data <- 
  domestic_violence %>% 
  group_by(wealth_index, exp_violence) %>% 
  count(wealth_index = factor(wealth_index)) %>% 
  ungroup() %>% 
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Bar Graph of Wealth

bargraph_wealth <- 
  ggplot(wealth_data) + # Use Subset without NA's
  aes(x = wealth_index, y = n, fill = exp_violence) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = my_palette) +
  geom_text(aes(label = paste0(round(pct, 1),"%")), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            colour = "white", 
            size = 3) +
  labs(x = "Wealth Index",
       y = "Number of Individulas (n)",
       title = "Domestic Violence across Wealth Index",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence, total_violence_na)),
       fill = "Domestic Violence?")


## Highest Education ----

## Highest Education Data

education_data <- 
  domestic_violence %>% 
  group_by(highest_education, exp_violence) %>% 
  count(highest_education = factor(highest_education)) %>% 
  ungroup() %>% 
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Bar Graph of education

bargraph_education <- 
  ggplot(education_data) + # Use Subset without NA's
  aes(x = highest_education, y = n, fill = exp_violence) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = my_palette) +
  geom_text(aes(label = paste0(round(pct, 1),"%")), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            colour = "white", 
            size = 3) +
  labs(x = "Highest Education",
       y = "Number of Individulas (n)",
       title = "Domestic Violence across Education Level",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence, total_violence_na)),
       fill = "Domestic Violence?")
  

## Combining ALL demographic plots together into one ----

combined_grids <- plot_grid(bargraph_age_group, bargraph_urban_rural, bargraph_wealth, bargraph_education, labels = "AUTO")


## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## 
## ~ Domestic Violence Plots ~ ----
##
## ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

## Calculating Women who ANSWERED to DV Questions

total_answered_dv <-
  sum(!is.na(domestic_violence$exp_violence))

total_answered_dv_na <- 
  ir_domestic_violence %>% 
  filter(is.na(exp_violence)) %>% # Missing Data 
  nrow()

percentage_na_violence <- 
  round(total_answered_dv_na/total_answered_dv * 100, digits = 1)

## Calculating women who reported EXPERIENCING DV

total_yes_dv <- 
  nrow(violence)

# Calculate percent of women who ANWERED that REPORTED DV
percent_yes_answered_dv <- 
  round(total_yes_dv/total_answered_dv * 100, digits = 1)

## Types of Domestic Violence ----

#Total women experienced domestic violence values
total_violence_type <- 
  sum(!is.na(domestic_violence$violence_type))

# Total missing Experienced Domestic Violence values

total_violence_type_na <-
  sum(is.na(domestic_violence$violence_type))

## Create subset data for types of violence

type_dv_data <- 
  domestic_violence %>% 
  filter(!is.na(violence_type)) %>% # Remove NA's 
  count(violence_type = factor(violence_type)) %>% 
  arrange(desc(n)) %>%
  mutate(pct = round(prop.table(n) * 100, digits = 1))


## Create bargraph for types of violence

bargraph_violence_type <- 
  ggplot(type_dv_data, 
         aes(x = violence_type, y = n)) + # Use Subset without NA's
  geom_segment(aes(x = reorder(violence_type, n), xend = violence_type, y= 0, yend = n, fill = "lightgrey")) +
  geom_point(size = 2.5,
             color = "#168aad") +
  coord_flip() +
  geom_text(aes(label = paste0(round(pct, 1),"%")), # Add percentage to each bar
            position = position_dodge(width = 0.9), 
            vjust = -1, 
            colour = "black", 
            size = 3) +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position="none") +
  labs(y = "Number of Individulas (n)",
       x = "",
       title = "Emotional vs. Physical vs. Sexual Violence",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_violence_type, total_violence_type_na)))

## Perpetrator ----

#Total women who answered if and who performed violence

total_perpetrator <- 
  sum(!is.na(perpetrator_violence$perpetrator))


# Total missing Experienced Domestic Violence values

total_perpetrator_na <-
  sum(is.na(perpetrator_violence$perpetrator)) 


## Create subset data for types of violence

perpetrator_data <- 
  perpetrator_violence %>% 
  filter(!is.na(perpetrator)) %>% # Remove NA's 
  count(perpetrator = factor(perpetrator)) %>% 
  arrange(desc(n)) %>%
  mutate(pct = round(prop.table(n) * 100, digits = 1))

# Create bargraph to represent physical perpetrator 

bargraph_perpetrator <- 
  ggplot(perpetrator_data, 
         aes(x = perpetrator, y = n)) + # Use Subset without NA's
  geom_segment(aes(x = reorder(perpetrator, n), xend = perpetrator, y= 0, yend = n, fill = "lightgrey")) +
  geom_point(size = 2.5,
             color = "#168aad") +
  coord_flip() +
  geom_text(aes(label = paste0(round(pct, 1),"%")), # Add percentage to each bar
            position = position_dodge(width = 0.9), 
            vjust = -1, 
            colour = "black", 
            size = 3) +
  theme_minimal() +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position="none") +
  labs(y = "Number of Individulas (n)",
       x = "",
       title = "Perpetrator of Women who Experienced Physical Violence",
       subtitle = sprintf(sprintf("N = %s, missing data = %s", total_perpetrator, total_perpetrator_na)))

```

# **Context**

Colombia has achieved important victories in the last two decades regarding the promotion of gender equality and women' empowerment, although there are still significant gaps to reduce.

According to the [UN Women website](https://lac.unwomen.org/en/donde-estamos/colombia), Indigenous and Afro-Colombian women have been affected disproportionately by violence derived from the conflict; among 3,445 cases of murder in Indigenous and Afro-Colombian individuals, 65.5% were women. Additionally, in a [UN country report](https://data.unwomen.org/features/covid-19-survey-violence-against-women-colombia-heralds-local-level-data-and-changes#:~:text=The%20survey%20conducted%20in%20Colombia,physical%20violence%2C%20denial%20of%20basic) measuring the violence against women during the COVID-19 confinement (pandemic), a survey conducted in Colombia of more than 1200 women between August and September demonstrated that violence against women was pervasive throughout the country, with **6 in 10 women (63%)** reporting that they or someone they know has experienced at least one form of violence.

The objective of this report is to descriptively analyse domestic violence against women in Colombia.

# **Data set Description**

The data set used in this report is a subset of the **Demographic and Health Surveys (DHS)**. The DHS are a series of standardized surveys conducted periodically in developing countries that collect data on various aspects of population, health, and nutrition. These surveys, which are funded by the United States Agency for International Development (USAID), are a gold-standard source of reliable public health data for many countries and international bodies.

The included subset is part of the *women's recode dataset*. It contain individual-level data on women aged 15 to 49 in the surveyed households, from Colombia.

# **Sample Characteristics**

Out of `r num_participants` surveyed individuals, a total of `r num_domestic_violence` (`r percent_domestic_violence`%) were included in the domestic violence module. From that subset of participants, `r total_violence` women answered to some sort of question on domestic violence (emotional, physical, or sexual). Overall, out of the women who answered, a total of `r total_yes_dv` women (`r percent_yes_answered_dv`%) reported experiencing some sort of domestic violence.

*It is important to take note of the important and relatively high amount of missing values (NA) in questions related to domestic violence.* 

### Distribution of Domestic Violence in Women by Demographics

Based on the sample of women interviewed for the domestic violence module, the majority of women reported **NOT** experiencing domestic violence. A similar pattern can be seen through different demographics (e.g. age groups, urban vs. rural, wealth index, or education level).

```{r combined plots, fig.width=15, fig.height=10, fig.cap= "Figure 1. Domestic Violence Distribution across Various Demographic Variables"}

## Combining ALL demographic plots together into one ----

combined_grids <- plot_grid(bargraph_age_group, bargraph_urban_rural, bargraph_wealth, bargraph_education, labels = "AUTO")

print(combined_grids)

```

<br>

# **Domestic Violence: Descriptive Analysis**

### Types of Domestic Violence

To better understand the type of domestic violence experienced in women who **reported experiencing** some sort of domestic violence, Figure 2 breaks down the different types of domestic violence and their reported percentage. 

*CAUTION: Note the amount of missing values*

Based on Figure 2, the three main types of domestic violence reported by Colombian women are emotional and physical violence, physical violence alone, and emotional violence alone.

```{r dv_type plot, fig.cap= "Figure 2. Domestic Violence Distribution by Type"}

print(bargraph_violence_type)

```

<br>

### Perpetrators

When asking to identify the perpetrator (for physical violence ONLY), fewer women answered. Overall, 90.9% of respondents did not identify any of the given options as a perpetrator (mother, children, relative, current boyfriend, or former boyfriend). For the respondents that did identify someone, 6.7% identified family members (mother, children, other relative), 1.9% identified partners (current boyfriend, former boyfriend), and only 0.5% identified **both** family member **and** partner.

```{r perpetrator plot, fig.cap= "Figure 3. Reported Perpetrators"}

print(bargraph_perpetrator)

```

<br>

# **Conclusion**

Overall, `r percent_yes_answered_dv`% of women surveyed reported some sort of domestic violence. When looking at the distribution of domestic violence by demographics, no specific factor or pattern was identified.

A high number of missing values were identified to questions related to domestic violence. This might be due to the fact that some participants did not want to answer those sensitive questions. Due to the high number of missing values, the results above have to be carefully analysed and interpreted.

