---
title: "Workshop: Transforming, selecting, filtering, and plotting"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: true
    number_sections: false
author: "Author's name here"
date: "2023-06-14"
editor_options: 
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Load packages and data

To get started, **load in the needed packages**: {tidyverse}, {here},
and {esquisse}.

```{r}
"WRITE_YOUR_CODE_HERE"
```

Now, **read the dataset into your RStudio environment**. The data frame
you import should have 142 rows and 9 columns. Remember to use the
`here()` function to use project-relative paths.

```{r}
"WRITE_YOUR_CODE_HERE"
```

Next, view your dataset and compare it to the variable definitions (open
the "00_info_about_the_dataset" file in the "data folder).

# Clean data with {dplyr}

## **Step 1**: Examine and clean dataset

Before jumping into wrangling or plotting, let's think about the types
of variables in our dataset. Take note of which variables should be
numeric and which should be factors.

Now let's check that R has classified these variables correctly. You can
check the data classes assigned to each variable with `summary()` or
`glimpse()`.

```{r}
"WRITE_YOUR_CODE_HERE"
```

Notice that some of your variables are of class "character", but they
should be numeric (e.g. `bmi`). This is because those variables have
some words in them in addition to number. Can you spot those words when
you view the dataset?

Other variables of class "character" should be factors. Lastly, some
variables that are "numeric" should be integers.

We need to change these variables to correct type, because this will be
essential for further manipulations and for plotting!

Use `mutate()` to convert your variables into the right type.

```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

**Hint**: two variables need to be converted to integer, three to
factor, and four to numeric. You may get a warning message about your
numeric columns. This is telling you that some NAs were introduced to
the data. This is not a problem in this case, so you can disregard the
message.

Now that you have converted them, use `summary()` or `glimpse()` again
to check that the data classes are correct. Notice that in your new
numeric columns, the text that used to be there as been replaced with
`NA` (this is what the warning message was about).

## **Step 2**: Convert the physical activity variables

Currently, the variables of physical activity are in seconds per day.
There are 3 types of physical activity variables: sedentary behavior (`sedentary_ap_s_day`), light physical activity
(`light_ap_s_day`), and moderate to vigorous physical activity
(`mvpa_s_day`). These variables are measured in seconds per day.
However, the [WHO
recommendations](https://apps.who.int/iris/bitstream/handle/10665/337001/9789240014886-eng.pdf)
for physical activity are in minutes per week, so we want to align with
these measures. To do this, complete the following manipulations:

1.  Convert these numerical variables from **seconds/day** to
    **minutes/week**. (Hint: use `mutate()` to create new variables that
    are in minutes per week. As a kind reminder, 60 seconds = 1 minute
    and 7 days = 1 week.)

2.  Remove the previous seconds per day variables. (Hint: you can
    use `ends_with()` within the `select()` function.)

```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

Lastly, rename `oms_recommendation` to `who_recommendation` (OMS is
French for WHO).

```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

You will use this `obesity_data_cleaned` for all the following steps.

## **Step 3**: Combine physical activity variables

Create a new column that adds light physical activity with moderate to
vigorous physical activity. This should give us the total amount of
activity in minutes per week.

```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

# Visualize data with {esquisse}

## **Plot 1**: Histogram

Histograms are used to visualize the distribution of a single numeric
(continuous) variable. Chose a variable from the dataset that you can
plot a histogram with.

Using esquisse, create your histogram.

```{r}
"PASTE_THE_ESQUISSE_CODE_HERE"
```

Note: Sometimes code generated by esquisse can have unwanted filtering. This is due to a bug in the package. Double check your code and remove any extra `filter()` operations. 

## **Plot 2**: Boxplot

Boxplots are used to visualize the distribution of a numeric variable,
split by the values of a discrete variable.

Use esquisse to create a boxplot to show the distribution of a numeric
variable (the same one used for your histogram) and plot it against a
categorical variable from the dataset. Set fill color to match the
values of your categorical variable.

```{r}
"PASTE_THE_ESQUISSE_CODE_HERE"
```

# Wrap up

That's it for this assignment! We will choose 2-3 people to present your work during the workshop. If you would like to share your results with the class, please let an instructor know.

# Bonus challenge (optional)

Finished early? Try some new manipulations with `mutate()` below. 

## Replace values in a selected column

```{r}
# Example: replace values in the sex column
obesity_data_cleaned %>% mutate(sex = str_replace(sex, "M", "Male"),
                                sex = str_replace(sex, "F", "Female"))
```

Now perform a similar transformation on the `status` variable, to change "Aldulte" and "Enfant" to "Adult" and "Child".
```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

## Replace using dplyr mutate_if()

We can use `mutate_if()` to update the column values conditionally. The following example applies the `toupper()` function to all factor variables. 
```{r}
# Example: turn all text variables to ALL CAPS
obesity_data_cleaned %>% mutate_if(is.factor, toupper)
```
Note: the `toupper()` function converts factor variables to character. If we wanted to change them back to factor, you can use `mutate_if()` again and apply `as.factor()` to all character variables. 

Now perform a similar transformation to all numeric variables. You can apply the `round()` function to round the values to a set number of decimal places.

Hint: this time you will need to add 3 arguments to `mutate_if()` - the condition, the function, and the number of decimal places.
```{r}
obesity_data_cleaned <- "WRITE_YOUR_CODE_HERE"
```

