---
title: "Workshop 8: Grouping and Pivoting"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: true
    number_sections: true
author: "Author's name here"
date: "2023-06-28"
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Load packages and data

To get started, **load in the needed packages**: {tidyverse}, {here},
and {esquisse}.

```{r}
#Load packages
"WRITE_YOUR_CODE_HERE"
```

Now, **read the dataset into R**. The data frame you import should have
61 rows and 9 columns. Remember to use the `here()` function to allow
your Rmd to use project-relative paths.

```{r}
#Load dataset
diet_raw <- "WRITE_YOUR_CODE_HERE"
```

**Checkpoint:** Pay close attention to variable names in the data frame!
Although the variables are consistently named, notice that there are [no
neat separators]{.underline}. This will be important in later steps of
the assignment so keep this detail in mind.

# 1 More Practice Using `dplyr` Verbs!

NOTE: Keep in mind that the raw dataset is in a WIDE format while you
complete Exercise 1.

## Exercise 1: Dietary Intake of Households

### 1.1
Measurements for energy as well as the water, fat, and dry content of
foods were recorded during the first and second visit of households. Use
`dplyr` verbs to calculate the total energy, water, fat, and dry content
of foods consumed per household. You should have 4 new variables in the end.

```{r}
diet_clean1 <- diet_raw %>% "WRITE_YOUR_CODE_HERE"
```

**Checkpoint:** The original dataset had 9 columns. You should now have a total of 13 columns in your dataset! Note that the number of rows should remain unchanged.

### 1.2

Determine which 2 households which had the highest fat intake. HINT: Consider the `arrange()` function.

```{r}
diet_clean2 <- diet_clean1 %>% "WRITE_YOUR_CODE_HERE"
```

Household ID 1: 
Household ID 2:

# 2 Pivoting the Dataset

## Exercise 2: Wide to Long format

We will now pivot the raw data frame into a long format using the `pivot_longer()`
function. This will be a more complex pivot than you are used to, so we will guide you here.

Let's start by renaming the variables to include a neat separator:

### 2.1
```{r eval = F}
# Rename variable using the rename function
diet_raw_renamed <- 
  diet_raw %>% 
  rename(enerc_kcal__w_1 = enerc_kcal_w_1, 
         enerc_kcal__w_2 = enerc_kcal_w_2,
         dry__w_1 = dry_w_1,
         dry__w_2 = dry_w_2,
         water__w_1 = water_w_1,
         water__w_2 = water_w_2,
         fat__w_1 = fat_w_1,
         fat__w_2 = fat_w_2)
```

With these new renamings, we now have a unique symbol `__` that separates our variable types (fat, water, dry...) from the variable weeks.

We can now perform a complex pivot:

```{r}
# Pivot into a long data frame
diet_long <- 
  diet_raw_renamed %>% 
  pivot_longer(cols = 2:9, 
               names_sep = "__", 
               names_to = c(".value", "week"))
```

With this new dataset, we now have one row for each household-week.

To learn more about this kind of advanced pivot, we have prepared a short written lesson here: 
https://the-graph-courses.github.io/data_untangled_wp/lessons/ls08_advanced_pivoting.html

### 2.2 Basic data analysis with a long format dataset

Now, for each household, we would like to calculate the following: 

  - Average energy content of food
  - Average dry content of food
  - Average water content of food 
  - Average fat content of food 
  
Use the `group_by()` function to group by household and the `summarise()` function to obtain these summary statistics.

```{r}
summary_diet_long <- diet_long %>% "WRITE_YOUR_CODE_HERE"
```

HINT. Your code should look like this:

```{r eval = F}
diet_long %>% 
  GROUPING_FUNCTION_HERE(household_id) %>% 
  SUMMARY_FUNCTION_HERE(mean_enerc_kcal = mean(enerc_kcal),
                        ...)
```


### 2.3 Visualize data with {esquisse}

Using `esquisse`, plot the mean energy content vs. mean fat content of food consumed for all households.

```{r}
"PASTE THE ESQUISSE CODE HERE"
```

# Wrap up

That's it for this assignment! We will choose 2-3 people to present your
work during the workshop. If you would like to share your results with
the class, please let an instructor know.

# Submission: Upload Rmd file

Don't forget to save your answers and upload your assignment Rmd on the
workshop webpage. You should upload just one Rmd file with your answers
(do not upload the knitted HTML or a zipped folder). Make sure to
include your name in the YAML header at the top of the script.
