---
title: 'Solutions to Workshop 2 exercise: Catching errors'
output:
  html_document:
    number_sections: true
    toc: true
  word_document:
    toc: true
editor_options:
  markdown:
    wrap: 100
  canonical: true
  chunk_output_type: inline
---

```{r, include = FALSE, warning = FALSE, message = FALSE}
# Load packages 
if(!require(pacman)) install.packages("pacman")
pacman::p_load(knitr, here)

knitr::opts_chunk$set(error = T)

options(repos = list(CRAN="http://cran.rstudio.com/"))
```

# Solutions to Workshop 1 exercise: Catching errors



## PACKAGES AND FUNCTIONS

### Problem 1A

The code below tries to load the 'dplyr' package using the `p_load()` function from the `pacman` package

```{r}
# Incorrect code:
pacman:p_load(dplyr)

```
### Solution 1A

There should be double colons (`::`) between package name and function name
```{r}
# Corrected code:
pacman::p_load(dplyr)
```
Outcome: the `dplyr` package is loaded

### Problem 1B

The `cowsay` package is an R package that allows printing of character strings as messages from animals in your console. 
The code below tries to load the `cowsay` package, but there is a problem

```{r}
# Incorrect code:
install.packages(cowsay)
cowsay::say("Welcome to GRAPH Courses!")
```
### Solution 1B
Package name in `install.packages()` should be enclosed in quotes.
```{r message=FALSE}
# Corrected code:
install.packages("cowsay")
```
Now the `cowsay` package is installed, so the following code will work:
```{r message=FALSE}
cowsay::say("Welcome to GRAPH Courses!")
```

## STRING MANIPULATION

Each block of code in this section attempts to perform a string manipulation, but contains an error. Identify and correct these errors.

### Problem 2A

The code below tries to concatenate (join) two strings.
```{r}
# Incorrect code:
first_name <- Ash
# Message: "Error: object 'Ash' not found"
last_name <- Ketchum
# Message: "Error: object 'Ketchum' not found"
paste(first_name, last_name)
# Message: "Error: object 'first_name' not found"
```

### Solution 2A

Strings should be enclosed in quotes.
```{r}
# Corrected code:
first_name <- "Ash"
last_name <- "Ketchum"
```

The two text strings have been assigned to objects (see your Environment tab), so now the `paste()` function will recognize and concatenate them. 
```{r}
paste(first_name, last_name)
```

### Problem 2B

The code below tries to combine (join) two strings into one.
```{r}
# Incorrect code:
first_name <- "John"
last_name <- "Doe"
full_name <- first_name + last_name
full_name
```

### Solution 2B

Use `paste()` instead of the plus sign (`+`) to join strings.
```{r}
# Corrected code:
first_name <- "John"
last_name <- "Doe"
full_name <- paste(first_name, last_name)
full_name
```

## ARITHMETIC

### Problem 3A

A patient took 12000 steps on Monday and 15000 steps on Tuesday. The code below tries to calculate the average number of steps taken by a patient. 

```{r}
# Incorrect code:
steps_monday <- 12000
steps_tuesday <- 15000
average_steps <- steps_monday + steps_tuesday / 2
average_steps
```
The code runs without giving an error, but the result is incorrect. The average of 12000 and 15000 is not 19500.

### Solution 3A

Parentheses are needed around the sum of steps before dividing by 2.
```{r}
# Corrected code:
steps_monday <- 12000
steps_tuesday <- 15000
average_steps <- (steps_monday + steps_tuesday) / 2
average_steps
```

### Problem 3B
There are 500 smokers in a population of 20000. The code below attempts to calculate the percentage of smokers in the population. 
```{r}
# Incorrect code:
total_population <- 20000
smokers <- 500
percentage_smokers <- (smokers รท total_population) * 100
percentage_smokers
```

### Solution 3B
Use slash (`/`) instead of the division symbol (รท).
```{r}
# Corrected code:
total_population <- 20000
smokers <- 500
percentage_smokers <- (smokers / total_population) * 100
percentage_smokers
```


## NAMING R OBJECTS

Each block of code in this section attempts to create an R object, but contains an error related to the rules for naming R objects. Identify and correct these errors.

### Problem 4A

```{r}
# Incorrect code:
1st_student <- "John Doe"
1st_student
```
Object names cannot start with a number.

### Solution 4A

```{r}
# Corrected code:
first_student <- "John Doe"
first_student
```

### Problem 4B

```{r}
# Incorrect code:
total population <- 10000
total population
```
Object names cannot contain spaces.

### Solution 4B
```{r}
# Corrected code:
total_population <- 10000
total_population
```
This is just one possible solution. You can use period case (e.g., `total.population`) or camel case (e.g., `totalPopulation`) to name objects. 

### Problem 4C

```{r}
# Incorrect code:
R-object <- "Sample data"
R-object
```
Object names cannot contain hyphens.

### Solution 4C

```{r}
# Corrected code:
R_object <- "Sample data"
R_object
```

## INCORRECT FUNCTION USAGE 

Each block of code attempts to call a function, but contains an error. 
Identify and correct these errors.

### Problem 5A
```{r}
# Incorrect code:
sqrt("16")
```

### Solution 5A
The argument should be a numeric value, not a character.
```{r}
# Corrected code:
sqrt(16)
```

### Problem 5B
The code below tries to calculate the square root of a number.
```{r}
# Incorrect code:
sqrt[16]
```

### Solution 5B
Use parentheses instead of square brackets for function calls.
```{r}
# Corrected code:
sqrt(16)
```

### Problem 5C
The code below tries to get the first 5 rows of the `iris` dataframe.
```{r}
# Incorrect code:
head(5, iris)
```
The arguments are in the wrong order and they are not named.

### Solution 5C
R expects the first argument of the `head()` function to be the object you want to return (`iris` dataframe) and the second should be the number of rows.
```{r}
# Corrected code:
head(iris, 5)
```

If you name the arguments, the order no longer matters.
```{r}
# Alternate solution:
head(n = 5, x = iris)
```

## OBJECT NOT FOUND

Each block of code in this section attempts to use an R object, but contains an error because the object is not found. Identify and correct these errors.

### Problem 6A
The code below tries to calculate the mean of a sequence of tumor sizes.
```{r}
# Incorrect code:
tumor_sizes_in_cm <- c(1, 4, 2, 1, 3)
mean(tumor_sizes_1n_cm)
```
NOTE that `c()` is a function to combine the items together. It is correct code. The problem is in the second line.

### Solution 6A
Fix the typo in the object name (change `1` to `i`).
```{r}
# Corrected code:
tumor_sizes_in_cm <- c(1, 4, 2, 1, 3)
mean(tumor_sizes_in_cm)
```

### Problem 6B

The code below tries to plot the height of women in the `women` dataset.
```{r}
# Incorrect code:
Height_Women <- women$height
plot(Height__women)
```
The problem is in the second line.

### Solution 6B

Fix two types in the object name (lower case `w` should be  uppercase `W`, and there is an extra underscore `_`).
```{r}
# Corrected code:
Height_Women <- women$height
plot(Height_Women)
```

## FUNCTION NESTING/ INTERMEDIATE OBJECTS

Each block of code contains an error involving improper function nesting or intermediate objects.

### Problem 7A
The code below tries to use function nesting to plot the head (first 6 rows) of the `women` dataset. Identify and fix the error. 
CLUE: It involves function order.
```{r}
# Incorrect code:
head(plot(women))
```


### Solution 7A
The `plot()` function should be nested inside the `head()` function.
```{r}
# Corrected code:
plot(head(women))
```

### Problem 7B
The code below tries to plot the head (first 6 rows) of the `women` dataset by assigning an intermediate object. There is a problem on the second line though. Identify and fix it.
```{r}
# Incorrect code:
head_women <- head(women)
plot(head)
```

### Soltion 7B
The plot function should use the intermediate object (`head_women`) as its argument (not `head`).


```{r}
# Corrected code:
head_women <- head(women)
plot(head_women)
```

## MISSING OR MISPLACED CHARACTERS 


Each block of code contains an error involving a missing or misplaced character. Identify and correct these errors.

### Problem 8A

The code below tries to concatenate (join) two strings.
```{r}
# Incorrect code:
first_name <- "John"
last_name <- "Doe"
joined_name <- paste(first_name last_name)
joined_name
```
### Solution 8A
Add a comma between the two arguments in `paste()`
```{r}
# Corrected code:
first_name <- "John"
last_name <- "Doe"
joined_name <- paste(first_name, last_name)
joined_name
```

### Problem 8B
The code below tries to view the top 10 rows of the iris dataframe.

```{r}
# Incorrect code:
head(x = iris, n = 10))
```

### Solution 8B
Remove the extra closing parenthesis.
```{r}
# Corrected code:
head(x = iris, n = 10)
```

### Problem 8C
The code below tries to create an R object with a character value.

```{r}
# Incorrect code:
name <- toupper('John Doe")
```

### Solution 8C
Fix the mismatched quotes by changing them both to single `'` or double quotes `"`.
```{r}
# Corrected code:
name <- toupper("John Doe")
```

