---
title: "Workshop 7: Grouping, Summarizing and Plotting"
output:
  prettydoc::html_pretty:
    theme: architect
    toc: true
    number_sections: true
author: "Author's name here"
date: "2023-06-21"
editor_options: 
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Load packages and data

To get started, **load in the needed packages**: {tidyverse}, {here},
{janitor}, and {esquisse}.

```{r}
"WRITE_YOUR_CODE_HERE"
```

Now, **read the dataset into R**. The data frame you import should have
880 rows and 22 columns. Remember to use the `here()` function to allow
your Rmd to use project-relative paths.

```{r}
# Load dataset
"WRITE_YOUR_CODE_HERE"
```

The column names in this CSV have spaces in them, which is not
R-friendly. I would recommend using `janitor::clean_names()` to give
your variable names a clean and consistent format.

```{r}
# Clean variable names
tb_renamed <- "WRITE_YOUR_CODE_HERE"

```

**Checkpoint**: The dataframe should contain 880 rows and 21 columns
(see Environment tab). Column/variable names should be all lowercase
with no spaces. You can run `names(tb_renamed)` to print the variable
names.

# Investigating healthcare costs

## Step 1: Calculate a `total_cost` variable

There were three visits for the participants and each had a cost
(`first_visit_cost, second_visit_cost, third_visit_cost`). Add together
these costs to create a `total_cost` variable.

```{r}
tb_clean1 <- "WRITE_YOUR_CODE_HERE"
```

## Step 2: Summarize costs by group

Let's look at the costs by the sex of patients. Use `dplyr` verbs to
group by sex and summarize the median total cost.

```{r}
"WRITE_YOUR_CODE_HERE"

```

Next, summarize the mean cost of the first visit, for each first visit
location.

```{r}
"WRITE_YOUR_CODE_HERE"

```

## Step 3: Categorize total costs

Now we will create a `total_cost_categories` variable that reflects the
following classifications:

-   If the total cost is 0: the category is `free`.

-   If the total cost is less than 500: the category is `low`.

-   If the total cost is between 500 and 1000: the category is `medium`.

-   If the total cost is between 1000 and 3000: the category is `high`.

-   If the total cost is more than 3000: the total cost is `very high`.

(These are arbitrary definitions based on a quick review of the
distribution.)

```{r}
tb_clean2 <- "WRITE_YOUR_CODE_HERE"
```

# Encoding age groups

## Step 1: Create an `age_group` variable

The `age` variable records the age of each patient in years. For further
manipulations, we want to classify the patients into 4 equally-sized age
groups (i.e., the number of patients in each age group should be
approximately the same).

In order to determine what the age range for each age group should be,
we can use the `quantile()` function.

```{r}
quantile(tb_clean2$age)
```

We will now choose cutoffs for each age group based on these values.

**Create a new `age_group` variable with the following categories:**

-   18-36

-   37-47

-   48-57

-   58+

```{r}
tb_clean3 <- "WRITE_YOUR_CODE_HERE"

```

Now we can create a table of the `age_group` variable to see if we met
our goal of having a similar number of patients in each age group:

```{r}
# Tabulate age groups
tb_clean3 %>% tabyl(age_group)
```

**Checkpoint**: The if you classified the age groups correctly, you will
see that each age group has 24-26% of the patients.

## Step 2: Summarize costs by age and sex

Now we will summarize costs by mean, but this time use "nested"
grouping to group the data by two variables: `age_group` and `sex`.

```{r}
"WRITE_YOUR_CODE_HERE"

```

# Visualize data with {esquisse}

## **Plot 1**: Create a plot for the participants, by smoking habit

Create a plot of average total cost by age group, keeping only respondents who are smokers. You will first need to create a summary table and use that in esquisse. Make sure to choose an appropriate plot!

```{r}
"PASTE_THE_ESQUISSE_CODE_HERE"
```

## **Plot 2**: Total costs and Treatment initiation delay

Using `esquisse`, create a scatter plot of the treatment initiation
delay vs. the total costs, for all participants. Color the point by a categorical variable (Hint: drag a variable into the "Color" box).

```{r}
"PASTE_THE_ESQUISSE_CODE_HERE"
```

# Wrap up

That's it for this assignment! We will choose 2-3 people to present your
work during the workshop. If you would like to share your results with
the class, please let an instructor know.

If you finish early, see the instructor for bonus manipulations you can do with this dataset. 
